%-------------------------
% Resume in Latex
% Author : Jake Gutierrez
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumePositionSummary}[1]{
  \item\small{
    {#1 \vspace{-8pt}}
  }
}


\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%----------HEADING----------
% \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
%   \textbf{\href{http://sourabhbajaj.com/}{\Large Sourabh Bajaj}} & Email : \href{mailto:sourabh@sourabhbajaj.com}{sourabh@sourabhbajaj.com}\\
%   \href{http://sourabhbajaj.com/}{http://www.sourabhbajaj.com} & Mobile : +1-123-456-7890 \\
% \end{tabular*}

\begin{center}
    \textbf{\Huge \scshape Danylo Svatyuk} \\ \vspace{1pt}
    \small +447901615486 $|$ \href{mailto:danylo.svatyuk@gmail.com}{\underline{danylo.svatyuk@gmail.com}} $|$ 
    \href{https://www.linkedin.com/in/danylo-svatyuk/}{\underline{linkedin.com/in/danylo-svatyuk}}
\end{center}


%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Senior Software Engineer}{Jan 2022 -- Present}
      {\href{https://dashfinancial.com/}{\underline{Dash Financial Technologies}}}{Remote, United Kingdom}
      \resumePositionSummary{Order Management System for institutional options traders.}

      \resumeItemListStart
        \resumeItem{Creator and owner of authentication and authorization components of the system. \\
        Developed workflows for login, MFA, password recovery, user onboarding, access and permissions management etc. \\
        Implemented single-sing-on via SAML integration for enterprise clients.}
        \resumeItem{Parallelized workflows in core order processing module which increased throughput by 30\% per instance.}
        \resumeItem{Enhanced real-time client updates through WebSockets during demanding workflows by implementing aggregation, throttling, and parallel processing techniques for event streams, resulting in a shift from seconds to subseconds p99\textsuperscript{th} latencies.}
        \resumeItem{Designed and implemented users and orders audit trail system which enabled thorough inspection of user actions in the system and their effects on orders lifecycle.}
      \resumeItemListEnd
      
% -----------Multiple Positions Heading-----------
%    \resumeSubSubheading
%     {Software Engineer I}{Oct 2014 - Sep 2016}
%     \resumeItemListStart
%        \resumeItem{Apache Beam}
%          {Apache Beam is a unified model for defining both batch and streaming data-parallel processing pipelines}
%     \resumeItemListEnd
%    \resumeSubHeadingListEnd
%-------------------------------------------

    \resumeSubheading
      {Senior Software Engineer}{Aug 2020 --  Jan 2022}
      {\href{https://everymatrix.com/}{\underline{EveryMatrix}}}{Lviv, Ukraine}

      \resumePositionSummary{B2B SaaS platform for online gambling and betting.}

      \resumeItemListStart
        \resumeItem{Direct communication with clients during expansion into one of the biggest of European gambling markets. Translating legislative requirements into technical design.}
        \resumeItem{Contributed to platform's architecture committee, authored and reviewed multiple ADRs, RFCs, and tech design docs.}
        \resumeItem{Designed and executed product-wide technical solutions: research, PoC, single-service integration, "How to" docs, and cross-team knowledge sharing.}
        \resumeItem{Leveraged Kubernetes, Kafka, Istio, Kiali, and Argo CD to transform outdated monolithic architecture into a resilient, scalable event-driven microservices platform.}
      \resumeItemListEnd

    \resumeSubheading
      {Senior Software Engineer}{Nov 2019 -- July 2020}
      {\href{https://www.populusfinancial.com/}{\underline{Populous Financial Group}} contractor through \href{https://eleks.com/}{\underline{ELEKS}}}{Lviv, Ukraine}
      \resumePositionSummary{Developed back-end of modern mobile banking application.}
      \resumeItemListStart
        \resumeItem{Work in fast moving startup-like environment.}
        \resumeItem{Building best possible solution with limited time and dev resources.}
      \resumeItemListEnd

      \resumeSubheading
      {Software Engineer}{Apr 2017 -- Nov 2019}
      {\href{https://www.solarwinds.com/}{\underline{SolarWinds}} contractor through \href{https://www.softserveinc.com/en-us}{\underline{SoftServe}}}{Lviv, Ukraine}
      \resumePositionSummary{Solution for enterprise IT infrastructure management and monitoring.}
      
      \resumeItemListStart
        \resumeItem{Member of the core platform team focused on build pipeline, installation, configuration and update process of the solution.}
        \resumeItem{Accelerated the average build and test cycle time from 90 to 45 minutes by strategically decomposing the project into smaller modules which allowed to parallelize the build process.}
        \resumeItem{Reduced average size of files downloaded by installer by 30\% by downloading only required modules.}
        \resumeItem{Reduced downtime during major upgrades from hours to tens of minutes with features like background download and parallelized modules configuration.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd


%-----------PROJECTS-----------
%\section{Projects}
%    \resumeSubHeadingListStart
%      \resumeProjectHeading
%          {\textbf{Gitlytics} $|$ \emph{Python, Flask, React, PostgreSQL, Docker}}{June 2020 -- Present}
%          \resumeItemListStart
%            \resumeItem{Developed a full-stack web application using with Flask serving a REST API with React as the frontend}
%            \resumeItem{Implemented GitHub OAuth to get data from user’s repositories}
%            \resumeItem{Visualized GitHub data to show collaboration}
%            \resumeItem{Used Celery and Redis for asynchronous tasks}
%          \resumeItemListEnd
%      \resumeProjectHeading
%          {\textbf{Simple Paintball} $|$ \emph{Spigot API, Java, Maven, TravisCI, Git}}{May 2018 -- May 2020}
%          \resumeItemListStart
%            \resumeItem{Developed a Minecraft server plugin to entertain kids during free time for a previous job}
%            \resumeItem{Published plugin to websites gaining 2K+ downloads and an average 4.5/5-star review}
%            \resumeItem{Implemented continuous delivery using TravisCI to build the plugin upon new a release}
%            \resumeItem{Collaborated with Minecraft server administrators to suggest features and get feedback about the plugin}
%          \resumeItemListEnd
%    \resumeSubHeadingListEnd


%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Lviv Polytechnic National University}{Lviv, Ukraine}
      {Masters in Applied Mathematics}{2014 --2019}
  \resumeSubHeadingListEnd

%
%-----------PROGRAMMING SKILLS-----------
\section{Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{English}{ - full working proficiency} \\
     \textbf{German}{ - intermediate.} \\

     \textbf{Programming languages}{: C\#, SQL (TSQL, Postgres), Python, Rust (as a hobby)} \\
     ASP .Net Core, AWS, Cloud, Redis, RabbitMQ, Docker, Kubernetes, Kafka, Istio, service mesh,
     unit testing, integration testing, OOP, microservices, event-driven, distributed systems, CI/CD, Git, 
     REST API, algorithms, Linux, architecture \\
     \href{https://www.credly.com/earner/earned/badge/667372fc-1f37-4743-8fe2-60b88c371f6e}{\underline{AWS Certified Solutions Architect - Associate}} \\
     \href{https://www.credential.net/ca157eb4-f685-43ed-a368-1d3c0944dde1}{\underline{Confluent Certified Developer for Apache Kafka}} \\
     \href{https://www.credly.com/badges/3649b5ba-fcf4-4a2b-a32a-0c798421e6ba}{\underline{Certified Kubernetes Application Developer}}
    }}
 \end{itemize}
%-------------------------------------------
\end{document}
